Automated topic naming to support cross-project analysis of software maintenance activities

### 2011-03-24 msr/msr2011.tex
- [X] The authors need to further demonstrate the utility of       labelled topics in practice. Is understanding why a system       evolved a key problem? If so, it should be justified with a       citation or numbers.       - citing the secret life of bugs in this case         where Dr. Aranda found that finding out why was really hard :)
Discuss features, fix wordnet stuff, respond to example criticism
    - [X] In supervised labeling (3.3) it has not been discussed what
          features of commit messages has been used in
          training/testing learners.
          - response: in super

Similarly, Mockus and Votta~\cite{Mockus00} studied a large-scale industrial change-tracking system. 
They also leveraged WordNet, but only for word roots as they felt the synonyms would be non-specific and cause errors, problems we also encountered. 
Mockus et al. had access to system developers, with whom they could validate their labels. 
Since we try to bridge different organizations, instead of a single project, these kind of interviews are infeasible (particularly in the distributed world of open-source software).

@@

% in our previous work~\cite{Hindle09ICSM}, as well as -- CITED a little too often (vanity cites!)
In Baldi et al.~\cite{Baldi2008}, topics are named manually: human experts read the highest-frequency members of a topic and assign a label accordingly. 
As discussed earlier, given the topic \emph{``listener change remove add fire''}, Baldi et al. would assign the label \emph{event-handling}. 
The labels are reasonable enough, but still require an expert in the field to determine them. 
Furthermore, these labels are project-specific, because they are generated from the data of that project. E.g., we might have a label called `Oracle' in the MySQL case, since Oracle owns MySQL. 
We do this differently.
%This paper does this differently. 
First of all, we automated the process of naming the topics. Secondly, we labelled topics with project-independent terms, in order to permit cross-project comparison.

@@

%\todo[inline]{* clarify the mailinglist stuff we did}
%\todo[inline]{This part doesn't make a lot of sense}
To construct these expanded word-lists, we used WordNet~\cite{Fellbaum1998}, an English-language ``lexical database'' that contains semantic relations between words, including common related forms (similar to word stemming), meronymy and synonymy. 
We then added Boehm's software quality model \cite{Boehm+:1976:ICSE}, and classified his eleven `ilities' into their respective ISO9126 NFRs. 
We did the same for the quality model produced by McCall et al. \cite{mccall1977}. 
We then did a simple random analysis of mailing list messages from an open source project, KDE. If we judged a given message to contain terms that were related to one of the NFRs in ISO9126, we added it to our word-list. This allowed us to expand our word-lists with more software-specific terms.
%Finally, we randomly analyzed two mailing lists from another software project to expand our set with domain-specific terms. 
% Less info is probably better here...
%For example, we add the term ``performance'' to the synonyms for \emph{efficiency}, since this term occurs in most mail messages that discuss efficiency.  Table \ref{tbl:wnsig} shows the labels (NFRs) and word-lists we used for matching.

@@

We used a suite of supervised classifiers, WEKA~\cite{weka09}. 
WEKA includes machine learning tools such as support vector machines and Bayes-nets. 
We also used the multi-labelling add-on for WEKA, Mulan~\cite{mulan}. %\footnote{\url{http://mlkd.csd.auth.gr/multilabel.html}}. 
Traditional classifiers map our topics to a single class, whereas Mulan allows for a mixture of classes per topic, which maps to what we observed while manually labelling topics.

@@

For both projects Bayesian techniques did the best out of a wide variety of machine learners tested. 
Our best learners, Discriminative Multinomial Naive Bayes, Naive Bayes  and Multinomial Naive Bayes  are all based on Bayes's theorem and all assume, naively, that the features are independent. 
The features we used are word counts per message. 
One beneficial aspect of this result is that it suggests we can have very fast training and classifying  since Naive Bayes can be calculated in $O(N)$ for $N$ features.
%http://nlp.stanford.edu/IR-book/html/htmledition/naive-bayes-text-classification-1.html

@@

\section{Understanding software maintenance activities} 
\label{sec:analysis}
% \todo[inline]{talk about this topic in one section}
% \todo[inline]{reference project name Nomen more}
%In order to test  our ROC values produced acceptable results, we now turn to
%\emph{applying} those techniques to understand software maintenance
%activities. 
%\todo[inline]{more on intro ... why should the reader care about
 % this. It needs to show how the stuff in the intro (applications) is
 % possible}
%%% XXX NEIL I don't get this.. VVVVV
%\todo[inline]{fix section headings}
As we mentioned in the introduction, a key issue in software maintenance is understanding \emph{why} a system has evolved the way it has. 
In this section we demonstrate the value of labelled topic extraction
in addressing this issue. 
% more why
Labelled topics address \emph{why}  because they show why changes
occurred rather than \emph{how}. 
The \emph{how} of a change is the change itself, the purpose or
\emph{why} is what we are after.
We investigate the history of the two large-scale database systems that we studied. 
We use our technique to show the topic of development efforts over time in each project.
%We evaluated two research questions using the ground truth data that we annotated by hand:
We motivated our investigation with two research questions:
\begin{enumerate}
\item \emph{Do NFR frequencies change over time?} If a particular NFR was of more interest at one point in the life-cycle than another, this suggests that development activity shifted focus. For example, if a developer expected to see a recent focus on \emph{reliability}, but instead \emph{usability} dominated, he or she might re-prioritize up-coming work items.
\item \emph{Do projects differ in their relative interest in NFRs?} A program manager would be interested in knowing whether a particular NFR, such as \emph{reliability}, was more important for one project than another. This could be to confirm the initial design goals, or to track the progress on that quarter's objectives.  
\end{enumerate}

>>>>

Similarly, Mockus and Votta~\cite{Mockus00} studied a large-scale industrial change-tracking system. 
Mockus and Votta leveraged WordNet~\cite{Fellbaum1998}, an English-language ``lexical database'' that contains semantic relations between words, including common related forms (similar to word stemming), meronymy and synonymy.
They only used WordNet for word roots as they felt the synonyms would be non-specific and cause errors, problems we also encountered. 
Mockus et al. had access to system developers, with whom they could validate their labels. 
Since we try to bridge different organizations, instead of a single project, these kind of interviews are infeasible (particularly in the distributed world of open-source software).

@@

% in our previous work~\cite{Hindle09ICSM}, as well as -- CITED a little too often (vanity cites!)
In Baldi et al.~\cite{Baldi2008}, topics are named manually: human
experts read the highest-frequency members of a topic and assign a
label accordingly. 
%XXX Possible to cut this
As discussed earlier, given the topic \emph{``listener change remove add fire''}, Baldi et al. would assign the label \emph{event-handling}. 
The labels are reasonable enough, but still require an expert in the field to determine them. 
Furthermore, these labels are project-specific, because they are generated from the data of that project. E.g., we might have a label called `Oracle' in the MySQL case, since Oracle owns MySQL. 
We do this differently.
%This paper does this differently. 
First of all, we automated the process of naming the topics. Secondly, we labelled topics with project-independent terms, in order to permit cross-project comparison.

@@

%\todo[inline]{* clarify the mailinglist stuff we did}
%\todo[inline]{This part doesn't make a lot of sense}
To construct these expanded word-lists, we used
WordNet~\cite{Fellbaum1998}.
%, an English-language ``lexical database'' that contains semantic relations between words, including common related forms (similar to word stemming), meronymy and synonymy. 
We then added Boehm's software quality model \cite{Boehm+:1976:ICSE}, and classified his eleven `ilities' into their respective ISO9126 NFRs. 
We did the same for the quality model produced by McCall et al. \cite{mccall1977}. 
We then did a simple random analysis of mailing list messages from an open source project, KDE. If we judged a given message to contain terms that were related to one of the NFRs in ISO9126, we added it to our word-list. This allowed us to expand our word-lists with more software-specific terms.
%Finally, we randomly analyzed two mailing lists from another software project to expand our set with domain-specific terms. 
% Less info is probably better here...
%For example, we add the term ``performance'' to the synonyms for \emph{efficiency}, since this term occurs in most mail messages that discuss efficiency.  Table \ref{tbl:wnsig} shows the labels (NFRs) and word-lists we used for matching.

@@

We used a suite of supervised classifiers, WEKA~\cite{weka09}. 
WEKA includes machine learning tools such as support vector machines and Bayes-nets. 
We also used the multi-labelling add-on for WEKA, Mulan~\cite{mulan}. %\footnote{\url{http://mlkd.csd.auth.gr/multilabel.html}}. 
Traditional classifiers map our topics to a single class, whereas Mulan allows for a mixture of classes per topic, which maps to what we observed while manually labelling topics.
The \emph{features} we used are word counts/occurrence  per topic, if
a word occurs frequently enough in a topic we consider it a feature of
the topic.

@@

For both projects Bayesian techniques did the best out of a wide variety of machine learners tested. 
Our best learners, Discriminative Multinomial Naive Bayes, Naive Bayes  and Multinomial Naive Bayes  are all based on Bayes's theorem and all assume, naively, that the features are independent. 
%The features we used are word counts per message. 
One beneficial aspect of this result is that it suggests we can have very fast training and classifying  since Naive Bayes can be calculated in $O(N)$ for $N$ features.
%http://nlp.stanford.edu/IR-book/html/htmledition/naive-bayes-text-classification-1.html

@@

\section{Understanding software maintenance activities} 
\label{sec:analysis}
% \todo[inline]{talk about this topic in one section}
% \todo[inline]{reference project name Nomen more}
%In order to test  our ROC values produced acceptable results, we now turn to
%\emph{applying} those techniques to understand software maintenance
%activities. 
%\todo[inline]{more on intro ... why should the reader care about
 % this. It needs to show how the stuff in the intro (applications) is
 % possible}
%%% XXX NEIL I don't get this.. VVVVV
%\todo[inline]{fix section headings}
As we mentioned in the introduction, a key issue in software maintenance is understanding \emph{why} a system has evolved the way it has~\cite{aranda09icse}. 
In this section we demonstrate the value of labelled topic extraction
in addressing this issue. 
% more why
Labelled topics address \emph{why}  because they show why changes
occurred rather than \emph{how}. 
The \emph{how} of a change is the change itself, the purpose or
\emph{why} is what we are after.
We investigate the history of the two large-scale database systems that we studied. 
We use our technique to show the topic of development efforts over time in each project.
%We evaluated two research questions using the ground truth data that we annotated by hand:
We motivated our investigation with two research questions:
\begin{enumerate}
\item \emph{Do NFR frequencies change over time?} If a particular NFR was of more interest at one point in the life-cycle than another, this suggests that development activity shifted focus. For example, if a developer expected to see a recent focus on \emph{reliability}, but instead \emph{usability} dominated, he or she might re-prioritize up-coming work items.
\item \emph{Do projects differ in their relative interest in NFRs?} A program manager would be interested in knowing whether a particular NFR, such as \emph{reliability}, was more important for one project than another. This could be to confirm the initial design goals, or to track the progress on that quarter's objectives.  
\end{enumerate}
